---
title: "Loudness Analysis"
author: "Patricio Moracho"
date: "26/10/2020"
output:
  md_document:
    variant: markdown_github
---

```{r, include=FALSE}
stopifnot(require(knitr))
options(width = 90)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  dev = "png",
  dpi = 150,
  fig.asp = 0.7,
  fig.width = 8,
  out.width = "80%",
  fig.align = "center"
)
library(loudness)
```

Package for loudness analysis. It performs a series of analyses from an audio file by first transforming it into a timeline with the loudness values. This package depends on the [ffmpeg](https://ffmpeg.org/) tool that should be previously installed.

First, we can load an audio file, to generate a `lutl` object, which is nothing more than, a series of loudness level observations per time.

```{r load}
library(loudness)

tl <- lutl_from_file('audio/R_MIC_200903-165318.mp3')
```

From the timeline, we can study the distribution of loudness levels: 

```{r density_plot, fig.width=10, fig.height=5, fig.align='center'}
loudness::plot_density(tl)
```

