---
title: "Loudness Analysis"
author: "Patricio Moracho"
date: "26/10/2020"
output:
  md_document:
    variant: markdown_github
---

```{r, include=FALSE}
stopifnot(require(knitr))
options(width = 90)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  dev = "png",
  dpi = 150,
  fig.asp = 0.7,
  fig.width = 8,
  out.width = "80%",
  fig.align = "center"
)
library(loudness)
```

# Loudness

Package for loudness analysis. It performs a series of analyses from an audio file by first transforming it into a timeline with the loudness values. This package depends on the [ffmpeg](https://ffmpeg.org/) tool that should be previously installed.

The length of the timeline will be from a tenth of a second to multiple hours, or days. The limit will be on the length of audio file that `ffmpeg` is able to process, the disk space, for the extraction of the LUFS values, the memory capacity to handle the amount of observations involved. As an example, about 24 hours of recording, are transformed into a lutl of 868899 observations and about 23 MB, processed in about 15 minutes

First, we can load an audio file, to generate a `lutl` object, which is nothing more than, a series of loudness level observations per time.

```{r load}
library(loudness)

tl <- lutl_from_file('audio/R_MIC_200903-165318.mp3')
```

The `lutl` objects like any other object in R can be saved and it is recommended to do so:

```{r save_lutl, eval=FALSE, fig.align='center', fig.height=5, fig.width=10}
saveRDS(tl, 'audio/R_MIC_201010-132132.Rds')
tl <- readRDS('audio/R_MIC_201010-132132.Rds')
```

```{r include=FALSE}
tl <- readRDS('audio/R_MIC_201010-132132.Rds')
```

From the timeline, we can study the distribution of loudness levels: 

```{r density_plot, fig.width=10, fig.height=5, fig.align='center'}
plot_density(tl)
```

You can also reproduce some part of the timeline

```{r play, eval=FALSE, fig.align='center', fig.height=5, fig.width=10}
play(tl)
```
We can also study loud sounds within a timeline

```{r plot_timeline, fig.width=10, fig.height=5, fig.align='center'}
plot_timeline(tl, percentil = 99)
```

### TO DO

* `play()` use real time (not file time)
